Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-14 resex.tex
Revised results on 8th-turn pulsing. Defined a set of figure widths.

\newcommand{\seventhtp}{7th-turn pulsing}
\newcommand{\eighthtp}{8th-turn pulsing}
\newcommand{\tenthtp}{10th-turn pulsing}

@@

@@

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.49\textwidth]{2016injerra2b2u_pattern_3_5um_intensity.png}
  &
\includegraphics[width=0.49\textwidth]{2016injerra2b2u_pattern_3_5um_sigm.png}
  \\
\includegraphics[width=0.49\textwidth]{2016injerra2b2u_pattern_3_5um_emit1.png} &
\includegraphics[width=0.49\textwidth]{2016injerra2b2u_pattern_3_5um_emit2.png}
  \\
\end{tabular}
\caption{Relative intensity (top left), bunch length (top right) and
  horizontal (bottom left) and vertical (bottom right) emittances for
  different pulsing patterns, calculated by distribution tracking
  based on the 2016 injection optics with
  $(Q_x, Q_y) = (64.28, 59.31)$ and standard lattice errors. The
  resonant and random excitations are applied in both planes, with an
  amplitude of 96~nrad. No random noise component is added. Because of
  its much larger effects, the random excitation is shown with
  separate vertical axes.}
\label{fig:patternsim}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    no excitation & $10^{\mathrm{th}}$, H+V \\
    \includegraphics[width=0.49\textwidth]{2016injnocolc15o+19_6noerru_dp0_ord10_annotate.png} &
    \includegraphics[width=0.49\textwidth]{2016injnocolc15o+19_6noerrut10skhv_dp0_ord10.png}
    \\
    7th, H & 7th, V \\
    \includegraphics[width=0.49\textwidth]{2016injnocolc15o+19_6noerrut7skh_dp0_ord7.png} &
    \includegraphics[width=0.49\textwidth]{2016injnocolc15o+19_6noerrut7skv_dp0_ord7.png} \\
  \end{tabular}
  \caption{Frequency-map analysis in betatron tune space based on the
    2016 injection optics with no machine errors and tunes (64.28,
    59.31): without excitation (top left); $10^{\mathrm{th}}$~turn
    pulsing in both horizontal and vertical planes (top left);
    \seventhtp\ in the horizontal (bottom left) and
    vertical (bottom right) planes. The excitation amplitude is
    120~nrad in the corresponding plane. The colors (blue to red)
    represent the tune jitter of tracked particles starting at each
    given location in tune space~\cite{fmalaskar}. The absence of a
    strong excitation of any resonance in case of vertical
    \seventhtp\ and the strong excitation in case
    of horizontal pulsing confirms the excitation of the $7 Q_x$
    resonance. For $10^{\mathrm{th}}$~turn pulsing, there is in
    contrast no significant difference between H, V, or H+V (see
    Appendix~\ref{app:sec:10}, Fig.~\ref{app:fig:fma:10}).}
  \label{fig:patternfma}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    no excitation & random, H+V \\
    \includegraphics[width=0.49\textwidth]{2016injerra2b2u_3_5um_hist_y.png} &
    \includegraphics[width=0.49\textwidth]{2016injerra2b2u_ranhv_3_5um_hist_x.png} \\
    7th, H+V & $10^{\mathrm{th}}$, H+V \\
    \includegraphics[width=0.49\textwidth]{2016injerra2b2u_t7skhv_3_5um_hist_x.png}
                  &
    \includegraphics[width=0.49\textwidth]{2016injerra2b2u_t10skhv_3_5um_hist_y.png} \\
  \end{tabular}
  \caption{Calculated beam distributions as a function of vertical
    position from distribution-tracking simulations based on the 2016
    injection optics with $(Q_x, Q_y) = (64.28, 59.31)$ and standard
    lattice errors: no excitation (top left), random excitation (top
    right), \seventhtp\ (bottom left), and
    \tenthtp\ (bottom right). The excitations
    are applied in both planes with an amplitude of 96~nrad. For each
    of the 4~cases, 3~plots are shown. The top plot shows the
    normalized transverse distributions: `initial' (after
    $10^2$~turns, in gray), `final' (after $10^4$~turns, in black),
    and their Gaussian fits (light and dark red, respectively). The
    middle plots show the relative residuals (i.e., differences, in
    percent of the peak value) between final and initial distributions
    (in black) and between each distribution and its Gaussian fit (in
    light and dark red). The ratios between final and initial
    distributions are drawn in black in the bottom plots. The
    residuals emphasize changes near the core of the distributions,
    whereas ratios (when statistically significant), reveal variations
    in the tails.}
  \label{fig:patternhist}
\end{figure*}

@@

\begin{figure*}
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{2016_bunch_intensity_v10th_no_damper_avg.png}&
    \includegraphics[width=0.32\textwidth]{2016_emith_avg_rel_v10th_no_damper.png}&
    \includegraphics[width=0.32\textwidth]{2016_emitv_avg_rel_v10th_no_damper.png}\\
  \end{tabular}
  \caption{Summary of the 2016 experiments on $10^{\mathrm{th}}$~turn
    pulsing in the vertical plane: losses (left), horizontal
    emittances (middle) and vertical emittances (right), relative to
    their initial values. The transverse damping system was not active
    in this case. The 3 excitation periods are labeled in black
    according to the value of the maximum excitation amplitude
    $A_{\mathrm{max}} = 5 \, \Delta A$: no excitation, 48~nrad or
    96~nrad. The 4~bunches experiencing the same excitation amplitude
    $n \, \Delta A$ ($n = 0, \ldots, 5$) are grouped by color. The
    data are averaged over the 4~bunches, with the envelope
    representing the standard deviation. The area with a blue
    background highlights qualitatively the fast adjustment period of
    the beam distribution, transitioning into a new equilibrium state
    (indicated by the gray background).}
  \label{fig:10thexp}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    Reference bunch, no excitation & Excited bunch, maximum amplitude \\
    \includegraphics[width=0.48\textwidth]{profile_v_10thv_slot_50.png} &
    \includegraphics[width=0.48\textwidth]{profile_v_10thv_slot_1300.png}\\
    \end{tabular}
    \caption{Vertical beam profiles measured with the Beam Synchrotron
      Radiation Telescope (BSRT) during the 2016 experiments on
      \tenthtp\ in the vertical plane. The
      transverse damping system was not active on these bunches. The
      beam distributions at the end of the excitation period are shown
      in black in the top plots, with a Gaussian fit in red. The
      bottom plots show the residuals: final profile minus initial
      profile (black); final profile minus its Gaussian fit
      (red). Residuals are expressed as a fraction of the peak profile
      amplitude. The black lines in the plots of the residuals are a
      measure of the overall change of the distribution shape. The red
      lines indicate how different the final distributions are from a
      Gaussian shape. Details of the analysis are given in
      Ref.~\cite{bsrtprofinj}. The distribution of the reference bunch
      (left) is almost unchanged, whereas the bunch experiencing the
      maximum excitation (right) shows a clear shift of particles from
      the axis towards approximately $\pm 2\sigma$.}
    \label{fig:10thexpprof}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_intensity.png} &
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2_rel.png} \\
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit1.png} &
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2.png} \\
  \end{tabular}	
  \caption{Simulations (with the distribution-tracking method) based
    on the 2016 injection optics with standard lattice errors and
    tunes $(Q_x, Q_y) = (64.28, 59.31)$: relative beam intensity (top
    left); normalized horizontal (bottom left) and vertical (bottom
    right) emittances; vertical emittance relative to its initial
    value (top right). The solid lines indicate the effect of
    \tenthtp\ in the vertical plane. The dotted
    lines include both the resonant excitation and a random dipole
    noise component of 6~nrad (in both horizontal and vertical
    planes).}
  \label{fig:10thsim}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{2016_scale_amp_10v_ran_lblshort_sim_prstab.png}
  \caption{Comparison between experiments and simulations of loss
    rates vs.\ resonant excitation amplitude for
    \tenthtp\ in the vertical plane. The
    relative average loss rate~$R$ is defined in
    Eq.~\ref{eqn:lossrate}. The experimental results for a maximum
    excitation amplitude of 48~nrad are shown in black and those for
    96~nrad are plotted in green (see also Fig.~\ref{fig:10thexp},
    left, for instance). The results with damper off are represented
    by solid dots, those with damper on are shown with open
    circles. The simulation results, including random dipole noise,
    are shown in red (see also Fig.~\ref{fig:10thsim}). Statistical
    and systematic uncertainties are discussed in the text. The curves
    represent empirical quadratic fits to the data with damper off
    (solid) and with damper on (dashed).}
  \label{fig:10thexploss}
\end{figure}

@@

\begin{figure*}
  \begin{tabular}{cc}
    no excitation & 7th, H+V \\
    \includegraphics[width=0.49\textwidth]{2017injnocolc15o+19_6noerru_dp0_ord14_annotate_7th.png} &
    \includegraphics[width=0.49\textwidth]{2017injnocolc15o+19_6noerrut7skhv_dp0_ord7.png} \\
    7th, H & 7th, V \\
    \includegraphics[width=0.49\textwidth]{2017injnocolc15o+19_6noerrut7skh_dp0_ord7.png} &
    \includegraphics[width=0.49\textwidth]{2017injnocolc15o+19_6noerrut7skv_dp0_ord7.png} \\
  \end{tabular}
  \caption{FMA in betatron tune space based on the 2017 injection
    optics with no machine errors and tunes (62.27, 60.295): without
    excitation (top left) and for \seventhtp\ in H+V (top right), H
    only (bottom left) and V only (bottom right). The excitation
    amplitude is 96~nrad. The $7 Q_x$, $7 Q_y$, and 14th-order
    $7 Q_x + 7 Q_y$ resonances are excited.}
  \label{fig:7th2017fma} 
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=0.49\textwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_intensity.png} &
    \includegraphics[width=0.49\textwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_rel_emit2.png} \\
    \includegraphics[width=0.49\textwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_emit1.png} &
    \includegraphics[width=0.49\textwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_emit2.png} \\
  \end{tabular}
  \caption{Calculated bunch intensities and emittances from
    distribution tracking based on the 2016 injection optics with
    standard errors and $(Q_x, Q_y) = (64.28, 59.31)$ and 2017
    injection optics with standard errors and
    $(Q_x, Q_y) = (62.27, 60.295)$: relative intensity (top left);
    horizontal emittance (bottom left); vertical emittance (bottom
    right); the relative vertical emittance is also shown (top
    right). The solid black line includes only a random dipole noise
    component in H+V of 6~nrad. The dotted and dashed lines correspond
    to \seventhtp\ with two different excitation amplitudes (24~nrad
    and 48~nrad), plus a random dipole noise component in H+V of
    6~nrad.}
  \label{fig:7thsim}
\end{figure*}

\begin{figure*}
  \begin{tabular}{ccc}
    \multicolumn{3}{c}{2016 experiment, 7th, H}	\\
    \includegraphics[width=0.32\textwidth]{2016_bunch_intensity_h7th_no_damper_avg.png} &
    \includegraphics[width=0.32\textwidth]{2016_emith_avg_rel_h7th_no_damper.png} &
    \includegraphics[width=0.32\textwidth]{2016_emitv_avg_rel_h7th_no_damper.png} \\
    \multicolumn{3}{c}{2017 experiment, 7th, H+V} \\
    \includegraphics[width=0.32\textwidth]{2017_bunch_intensity_hv7th_no_damper_avg.png} &
    \includegraphics[width=0.32\textwidth]{2017_emith_avg_rel_hv7th_no_damper.png} &
    \includegraphics[width=0.32\textwidth]{2017_emitv_avg_rel_hv7th_no_damper.png} \\
  \end{tabular}
  \caption{Measured losses and emittances during the 2016 and 2017
    experiments: relative losses (left), relative horizontal
    emittances (middle), and relative vertical emittances
    (right). Measurements are averaged over the bunches experiencing
    the same excitation amplitude. The transverse damping system was
    not active in this set of measurements.}
  \label{fig:7thexp}
\end{figure*}

@@

\begin{figure*}
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{2017_scale_amp_7h_lblshort.png} &
    \includegraphics[width=0.32\textwidth]{2017_scale_amp_7v_lblshort.png} &
    \includegraphics[width=0.32\textwidth]{2017_scale_amp_7hv_lblshort.png} \\
  \end{tabular}
  \caption{Comparison of the measured loss rates as a function of
    excitation amplitude during the 2017 experiment for \seventhtp\ in
    H only (left), V only (center), and in H+V (right). The three
    excitations generate similar loss rates.}
  \label{fig:7thexploss2017}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    Reference bunch, no excitation & Excited bunch, 7th, H+V \\
    \includegraphics[width=0.48\textwidth]{profile_v_7thhv_slot_2862.png} &
    \includegraphics[width=0.48\textwidth]{profile_v_7thhv_slot_2696.png} \\
  \end{tabular}
  \caption{Vertical beam profiles measured with the Beam Synchrotron
    Radiation Telescope (BSRT) during the 2017 experiments. The
    profiles are taken at the end of \seventhtp\ in H+V. For these
    bunches, the transverse damper was not active. The data is
    presented in the same way as in Fig.~\ref{fig:10thexpprof}. The
    profile changes in the bunch affected by the maximum excitation
    (right) are larger than those displayed by the reference bunch
    (left).}
  \label{fig:7thexpprof}
\end{figure*}

@@

\begin{figure*}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_intensity.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_sigm.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit1.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit2.png}
	\end{minipage}	
	\caption{\label{fig:8thsim} Relative intensity (top left), bunch length (top right), and horizontal (bottom left) and vertical (bottom right) emittance obtained from simulations (distribution tracking) based on the 2017 injection optics with standard errors and $(Q_x,Q_y)=(62.27,60.295)$. The solid line indicates an excitation with only a random dipole noise component in H+V of 6~nrad, and the dotted and dashed line the results for \eighthtp\ plus a random dipole noise component in H+V of 6~nrad.}
      \end{figure*}

\begin{figure*}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		no excitation
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerru_dp0_amp.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		$8^{\mathrm{th}}$ H+V
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerrut8skhv_dp0_amp_annotate.png}
	\end{minipage}	
	\caption{\label{fig:8th2017fmaamp} FMA analysis in amplitude space without excitation (left) and for \eighthtp\ (right) based on the 2017 injection optics with no machine errors and a tune of (62.27,60.295). The excitation is 96~nrad in both planes. The $16Q_y$ and \mbox{$8Q_x-4Q_y$} are both excited.}
\end{figure*}

% \begin{figure}
% 	\centering
% 	\includegraphics[width=1.0\linewidth]{2017_scale_amp_8hv_lblshort.png}
% 	\caption{\label{fig:8thexploss} Comparison of scaling of loss rates with excitation amplitude for \eighthtp\ in H+V measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars, the error on the loss rate is the error on the mean obtained through the average over the 6~bunches with the same excitation amplitude.}
% \end{figure}

\begin{figure*}
  \begin{tabular}{ccc}
  \includegraphics[width=0.32\textwidth]{2017_scale_amp_8h_lblshort.png} &
  \includegraphics[width=0.32\textwidth]{2017_scale_amp_8v_lblshort.png} &
  \includegraphics[width=0.32\textwidth]{2017_scale_amp_8hv_lblshort.png} \\
  \end{tabular}
  \caption{Comparison of scaling of loss rates with excitation
    amplitude for \eighthtp\ only in H (top), only in V (center) and
    in H+V (bottom) during the 2017 experiment. The excitation
    amplitude error is 15\% indicated by horizontal error bars. The
    vertical errorbars represent the pure statistical error based on
    the averaging over several bunches with the same excitation
    amplitude.}
  \label{fig:8thexploss2017}
\end{figure*}

>>>>

% abbreviations
\newcommand{\seventhtp}{7th-turn pulsing}
\newcommand{\eighthtp}{8th-turn pulsing}
\newcommand{\tenthtp}{10th-turn pulsing}

@@

% widths for figures
\newlength{\halfwidth}
\setlength{\halfwidth}{0.48\textwidth}
\newlength{\thirdwidth}
\setlength{\thirdwidth}{0.33\textwidth}
\newlength{\bsrtwidth}
\setlength{\bsrtwidth}{0.4\textwidth}
\newlength{\fmawidth}
\setlength{\fmawidth}{0.4\textwidth}

@@

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=\halfwidth]{2016injerra2b2u_pattern_3_5um_intensity.png}
  &
\includegraphics[width=\halfwidth]{2016injerra2b2u_pattern_3_5um_sigm.png}
  \\
\includegraphics[width=\halfwidth]{2016injerra2b2u_pattern_3_5um_emit1.png} &
\includegraphics[width=\halfwidth]{2016injerra2b2u_pattern_3_5um_emit2.png}
  \\
\end{tabular}
\caption{Relative intensity (top left), bunch length (top right) and
  horizontal (bottom left) and vertical (bottom right) emittances for
  different pulsing patterns, calculated by distribution tracking
  based on the 2016 injection optics with
  $(Q_x, Q_y) = (64.28, 59.31)$ and standard lattice errors. The
  resonant and random excitations are applied in both planes, with an
  amplitude of 96~nrad. No random noise component is added. Because of
  its much larger effects, the random excitation is shown with
  separate vertical axes.}
\label{fig:patternsim}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    no excitation & $10^{\mathrm{th}}$, H+V \\
    \includegraphics[width=\fmawidth]{2016injnocolc15o+19_6noerru_dp0_ord10_annotate.png} &
    \includegraphics[width=\fmawidth]{2016injnocolc15o+19_6noerrut10skhv_dp0_ord10.png}
    \\
    7th, H & 7th, V \\
    \includegraphics[width=\fmawidth]{2016injnocolc15o+19_6noerrut7skh_dp0_ord7.png} &
    \includegraphics[width=\fmawidth]{2016injnocolc15o+19_6noerrut7skv_dp0_ord7.png} \\
  \end{tabular}
  \caption{Frequency-map analysis in betatron tune space based on the
    2016 injection optics with no machine errors and tunes (64.28,
    59.31): without excitation (top left); $10^{\mathrm{th}}$~turn
    pulsing in both horizontal and vertical planes (top left);
    \seventhtp\ in the horizontal (bottom left) and
    vertical (bottom right) planes. The excitation amplitude is
    120~nrad in the corresponding plane. The colors (blue to red)
    represent the tune jitter of tracked particles starting at each
    given location in tune space~\cite{fmalaskar}. The absence of a
    strong excitation of any resonance in case of vertical
    \seventhtp\ and the strong excitation in case
    of horizontal pulsing confirms the excitation of the $7 Q_x$
    resonance. For $10^{\mathrm{th}}$~turn pulsing, there is in
    contrast no significant difference between H, V, or H+V (see
    Appendix~\ref{app:sec:10}, Fig.~\ref{app:fig:fma:10}).}
  \label{fig:patternfma}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    no excitation & random, H+V \\
    \includegraphics[width=\halfwidth]{2016injerra2b2u_3_5um_hist_y.png} &
    \includegraphics[width=\halfwidth]{2016injerra2b2u_ranhv_3_5um_hist_x.png} \\
    7th, H+V & $10^{\mathrm{th}}$, H+V \\
    \includegraphics[width=\halfwidth]{2016injerra2b2u_t7skhv_3_5um_hist_x.png}
                  &
    \includegraphics[width=\halfwidth]{2016injerra2b2u_t10skhv_3_5um_hist_y.png} \\
  \end{tabular}
  \caption{Calculated beam distributions as a function of vertical
    position from distribution-tracking simulations based on the 2016
    injection optics with $(Q_x, Q_y) = (64.28, 59.31)$ and standard
    lattice errors: no excitation (top left), random excitation (top
    right), \seventhtp\ (bottom left), and
    \tenthtp\ (bottom right). The excitations
    are applied in both planes with an amplitude of 96~nrad. For each
    of the 4~cases, 3~plots are shown. The top plot shows the
    normalized transverse distributions: `initial' (after
    $10^2$~turns, in gray), `final' (after $10^4$~turns, in black),
    and their Gaussian fits (light and dark red, respectively). The
    middle plots show the relative residuals (i.e., differences, in
    percent of the peak value) between final and initial distributions
    (in black) and between each distribution and its Gaussian fit (in
    light and dark red). The ratios between final and initial
    distributions are drawn in black in the bottom plots. The
    residuals emphasize changes near the core of the distributions,
    whereas ratios (when statistically significant), reveal variations
    in the tails.}
  \label{fig:patternhist}
\end{figure*}

@@

\begin{figure*}
  \begin{tabular}{ccc}
    \includegraphics[width=\thirdwidth]{2016_bunch_intensity_v10th_no_damper_avg.png}&
    \includegraphics[width=\thirdwidth]{2016_emith_avg_rel_v10th_no_damper.png}&
    \includegraphics[width=\thirdwidth]{2016_emitv_avg_rel_v10th_no_damper.png}\\
  \end{tabular}
  \caption{Summary of the 2016 experiments on $10^{\mathrm{th}}$~turn
    pulsing in the vertical plane: losses (left), horizontal
    emittances (middle) and vertical emittances (right), relative to
    their initial values. The transverse damping system was not active
    in this case. The 3 excitation periods are labeled in black
    according to the value of the maximum excitation amplitude
    $A_{\mathrm{max}} = 5 \, \Delta A$: no excitation, 48~nrad or
    96~nrad. The 4~bunches experiencing the same excitation amplitude
    $n \, \Delta A$ ($n = 0, \ldots, 5$) are grouped by color. The
    data are averaged over the 4~bunches, with the envelope
    representing the standard deviation. The area with a blue
    background highlights qualitatively the fast adjustment period of
    the beam distribution, transitioning into a new equilibrium state
    (indicated by the gray background).}
  \label{fig:10thexp}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    Reference bunch, no excitation & Excited bunch, maximum amplitude \\
    \includegraphics[width=\bsrtwidth]{profile_v_10thv_slot_50.png} &
    \includegraphics[width=\bsrtwidth]{profile_v_10thv_slot_1300.png}\\
    \end{tabular}
    \caption{Vertical beam profiles measured with the Beam Synchrotron
      Radiation Telescope (BSRT) during the 2016 experiments on
      \tenthtp\ in the vertical plane. The
      transverse damping system was not active on these bunches. The
      beam distributions at the end of the excitation period are shown
      in black in the top plots, with a Gaussian fit in red. The
      bottom plots show the residuals: final profile minus initial
      profile (black); final profile minus its Gaussian fit
      (red). Residuals are expressed as a fraction of the peak profile
      amplitude. The black lines in the plots of the residuals are a
      measure of the overall change of the distribution shape. The red
      lines indicate how different the final distributions are from a
      Gaussian shape. Details of the analysis are given in
      Ref.~\cite{bsrtprofinj}. The distribution of the reference bunch
      (left) is almost unchanged, whereas the bunch experiencing the
      maximum excitation (right) shows a clear shift of particles from
      the axis towards approximately $\pm 2\sigma$.}
    \label{fig:10thexpprof}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=\halfwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_intensity.png} &
    \includegraphics[width=\halfwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2_rel.png} \\
    \includegraphics[width=\halfwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit1.png} &
    \includegraphics[width=\halfwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2.png} \\
  \end{tabular}	
  \caption{Simulations (with the distribution-tracking method) based
    on the 2016 injection optics with standard lattice errors and
    tunes $(Q_x, Q_y) = (64.28, 59.31)$: relative beam intensity (top
    left); normalized horizontal (bottom left) and vertical (bottom
    right) emittances; vertical emittance relative to its initial
    value (top right). The solid lines indicate the effect of
    \tenthtp\ in the vertical plane. The dotted
    lines include both the resonant excitation and a random dipole
    noise component of 6~nrad (in both horizontal and vertical
    planes).}
  \label{fig:10thsim}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2016_scale_amp_10v_ran_lblshort_sim_prstab.png}
  \caption{Comparison between experiments and simulations of loss
    rates vs.\ resonant excitation amplitude for
    \tenthtp\ in the vertical plane. The
    relative average loss rate~$R$ is defined in
    Eq.~\ref{eqn:lossrate}. The experimental results for a maximum
    excitation amplitude of 48~nrad are shown in black and those for
    96~nrad are plotted in green (see also Fig.~\ref{fig:10thexp},
    left, for instance). The results with damper off are represented
    by solid dots, those with damper on are shown with open
    circles. The simulation results, including random dipole noise,
    are shown in red (see also Fig.~\ref{fig:10thsim}). Statistical
    and systematic uncertainties are discussed in the text. The curves
    represent empirical quadratic fits to the data with damper off
    (solid) and with damper on (dashed).}
  \label{fig:10thexploss}
\end{figure}

@@

\begin{figure*}
  \begin{tabular}{cc}
    no excitation & 7th, H+V \\
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerru_dp0_ord14_annotate_7th.png} &
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerrut7skhv_dp0_ord7.png} \\
    7th, H & 7th, V \\
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerrut7skh_dp0_ord7.png} &
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerrut7skv_dp0_ord7.png} \\
  \end{tabular}
  \caption{FMA in betatron tune space based on the 2017 injection
    optics with no machine errors and tunes (62.27, 60.295): without
    excitation (top left) and for \seventhtp\ in H+V (top right), H
    only (bottom left) and V only (bottom right). The excitation
    amplitude is 96~nrad. The $7 Q_x$, $7 Q_y$, and 14th-order
    $7 Q_x + 7 Q_y$ resonances are excited.}
  \label{fig:7th2017fma} 
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=\halfwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_intensity.png} &
    \includegraphics[width=\halfwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_rel_emit2.png} \\
    \includegraphics[width=\halfwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_emit1.png} &
    \includegraphics[width=\halfwidth]{2016+2017injerra2b2uran1_2e-3_7th_3_5um_emit2.png} \\
  \end{tabular}
  \caption{Calculated bunch intensities and emittances from
    distribution tracking based on the 2016 injection optics with
    standard lattice errors and $(Q_x, Q_y) = (64.28, 59.31)$ and 2017
    injection optics with standard lattice errors and
    $(Q_x, Q_y) = (62.27, 60.295)$: relative intensity (top left);
    horizontal emittance (bottom left); vertical emittance (bottom
    right); the relative vertical emittance is also shown (top
    right). The solid black line includes only a random dipole noise
    component in H+V of 6~nrad. The dotted and dashed lines correspond
    to \seventhtp\ with two different excitation amplitudes (24~nrad
    and 48~nrad), plus a random dipole noise component in H+V of
    6~nrad.}
  \label{fig:7thsim}
\end{figure*}

\begin{figure*}
  \begin{tabular}{ccc}
    \multicolumn{3}{c}{2016 experiment, 7th, H}	\\
    \includegraphics[width=\thirdwidth]{2016_bunch_intensity_h7th_no_damper_avg.png} &
    \includegraphics[width=\thirdwidth]{2016_emith_avg_rel_h7th_no_damper.png} &
    \includegraphics[width=\thirdwidth]{2016_emitv_avg_rel_h7th_no_damper.png} \\
    \multicolumn{3}{c}{2017 experiment, 7th, H+V} \\
    \includegraphics[width=\thirdwidth]{2017_bunch_intensity_hv7th_no_damper_avg.png} &
    \includegraphics[width=\thirdwidth]{2017_emith_avg_rel_hv7th_no_damper.png} &
    \includegraphics[width=\thirdwidth]{2017_emitv_avg_rel_hv7th_no_damper.png} \\
  \end{tabular}
  \caption{Measured losses and emittances during the 2016 and 2017
    experiments: relative losses (left), relative horizontal
    emittances (middle), and relative vertical emittances
    (right). Measurements are averaged over the bunches experiencing
    the same excitation amplitude. The transverse damping system was
    not active in this set of measurements.}
  \label{fig:7thexp}
\end{figure*}

@@

\begin{figure*}
  \begin{tabular}{ccc}
    \includegraphics[width=\thirdwidth]{2017_scale_amp_7h_lblshort.png} &
    \includegraphics[width=\thirdwidth]{2017_scale_amp_7v_lblshort.png} &
    \includegraphics[width=\thirdwidth]{2017_scale_amp_7hv_lblshort.png} \\
  \end{tabular}
  \caption{Comparison of the measured loss rates as a function of
    excitation amplitude during the 2017 experiment for \seventhtp\ in
    H only (left), V only (center), and in H+V (right). The three
    excitations generate similar loss rates.}
  \label{fig:7thexploss2017}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    Reference bunch, no excitation & Excited bunch, 7th, H+V \\
    \includegraphics[width=\bsrtwidth]{profile_v_7thhv_slot_2862.png} &
    \includegraphics[width=\bsrtwidth]{profile_v_7thhv_slot_2696.png} \\
  \end{tabular}
  \caption{Vertical beam profiles measured with the Beam Synchrotron
    Radiation Telescope (BSRT) during the 2017 experiments. The
    profiles are taken at the end of \seventhtp\ in H+V. For these
    bunches, the transverse damper was not active. The data are
    presented in the same way as in Fig.~\ref{fig:10thexpprof}. The
    profile changes in the bunch affected by the maximum excitation
    (right) are larger than those displayed by the reference bunch
    (left).}
  \label{fig:7thexpprof}
\end{figure*}

@@

\begin{figure*}
  \begin{tabular}{cc}
  \includegraphics[width=\halfwidth]{2017injerra2b2uran1_2e-3_8th_3_5um_intensity.png} &
  \includegraphics[width=\halfwidth]{2017injerra2b2uran1_2e-3_8th_3_5um_sigm.png} \\
  \includegraphics[width=\halfwidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit1.png} &
  \includegraphics[width=\halfwidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit2.png} \\
  \end{tabular}
  \caption{Calculated relative intensities (top left), bunch lengths
    (top right), horizontal emittances (bottom left), and vertical
    emittances (bottom right) from distribution-tracking simulations
    based on the 2017 injection optics with standard lattice errors
    and tunes $(Q_x, Q_y) = (62.27, 60.295)$. The solid black line is
    the reference case, including only a random dipole noise component
    in H+V of 6~nrad. The dotted and dashed lines are the results for
    \eighthtp, including the same random dipole noise component.}
  \label{fig:8thsim}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    No excitation & 8th, H+V \\
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerru_dp0_amp.png} &
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerrut8skhv_dp0_amp_annotate.png}
  \end{tabular}
  \caption{FMA in transverse amplitude space without excitation (left)
    and for \eighthtp\ (right) based on the 2017 injection optics with
    no lattice errors and tunes (62.27, 60.295). The excitation
    amplitude is 96~nrad in both planes. The $16 Q_y$ and
    \mbox{$8 Q_x - 4 Q_y$} resonances are excited.}
  \label{fig:8th2017fmaamp}
\end{figure*}

\begin{figure*}
  \begin{tabular}{ccc}
  \includegraphics[width=\thirdwidth]{2017_scale_amp_8h_lblshort.png} &
  \includegraphics[width=\thirdwidth]{2017_scale_amp_8v_lblshort.png} &
  \includegraphics[width=\thirdwidth]{2017_scale_amp_8hv_lblshort.png} \\
  \end{tabular}
  \caption{Measured loss rates vs.\ excitation amplitude for
    \eighthtp\ in H only (left), in V only (center) and in H+V (right)
    during the 2017 experiment. Uncertainties are statistical. The
    differences between the three data sets within each excitation
    mode (black, red, and yellow curves) provide an estimate of the
    systematic errors.}
  \label{fig:8thexploss2017}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    Reference bunch, no excitation & Excited bunch, 8th, H \\
    \includegraphics[width=\bsrtwidth]{profile_h_8thh_slot_804.png} &
    \includegraphics[width=\bsrtwidth]{profile_h_8thh_slot_632.png} \\
   \end{tabular}
   \caption{Horizontal beam profiles measured with the Beam
     Synchrotron Radiation Telescope (BSRT) during the 2017
     experiments. The profiles are taken at the end of the \eighthtp\
     in H. For these bunches, the transverse damper was not
     active. The data are presented in the same way as in
     Fig.~\ref{fig:10thexpprof}. The profile changes in the bunch
     affected by the maximum excitation (right) are larger than those
     displayed by the control bunch (left).}
   \label{fig:8thexpprof}
\end{figure*}
